Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an SI prefix signifying the \textit{Internal-Scenario}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the SE prefix denotes an \textit{External-Scenario}. Table IV.5 will explain the cases
system testing.

>>>>

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an \textbf{SI} prefix signifying the \textit{Scenario-Internal}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the \textbf{SE} prefix denotes an \textit{Scenario-External}. Table IV.5 will explain the cases
system testing.
